Deep Learning

### 2015-01-12 deepreview.tex
added boxes around the figures
fixed the {Frey} reference

\documentclass[]{article}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{natbib}

\parskip 0.1in
\parindent 0.0in
\setcounter{secnumdepth}{1}
\title{Deep Learning}

@@

Deep learning is currently making major advances in solving problems that
have resisted the best attempts of the Artificial Intelligence community
for many years. Deep learning is very good at discovering intricate
structure in large, high-dimensional datasets and is therefore widely
applicable in all of the sciences. For example, it has beaten previous
machine learning techniques at predicting the activity of potential drug
molecules~\citep{Dahl}, detecting new fundamental particles~\citep{particles},
classifying galaxies~\citep{??}, and predicting the effects of mutations in
non-coding DNA on gene expression and disease~\citep{Frey}.

@@

%%%%%%% GEOFF %%%%%%%%%%
GEOFF: Do box explaining backprop equatons
%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\centerline{
\includegraphics[width=0.33\linewidth]{chain-rule.pdf}
\includegraphics[width=0.33\linewidth]{forward-graph.pdf}
\includegraphics[width=0.33\linewidth]{backward-graph.pdf}
}
\caption{
Left: the chain rule of derivatives tells us how
two small effects (that of a small change of $x$ on $y$, and that of $y$ on $z$)
are composed. A small change $\Delta x$ in $x$
gets transformed first into a small change $\Delta y$ in $y$
by getting multiplied by $\frac{\partial y}{\partial x}$
(that is the definition of partial derivative). Similarly
that creates a change $\Delta z$ in $z$. Inserting one equation
into the other gives the chain rule of derivatives, i.e., how
$\Delta x$ gets turned into $\Delta z$ through multiplication
by the product of $\frac{\partial y}{\partial x}$ and
$\frac{\partial z}{\partial x}$. It also works when $x$, $y$
and $z$ are vectors (and the derivatives are Jacobian matrices). \newline
Middle: many computations, such as the succession of linear and non-linear 
transformations of multi-layer neural networks, can be described as
a graph where each node $i$ computes a quantity $u_i$ (e.g. the
output of an artificial neuron or the value of a parameter such as
a synaptic weight), based on the set of values $a_i$, composed of elements $u_j$ of
predecessors in the graph, i.e., $u_i = f_i(a_i)$. \newline
Right: the chain rule can be generalized to such computational
flow graphs by recursively computing the derivative of the final
node $u_N$ (e.g., the error to be minimized or the output of the neural network)
with respect to every internal node. The basic recursive equation
is
$\frac{\partial u_N}{\partial u_j} = \sum_{i: j \in a_i} \frac{\partial u_N}{\partial u_i}
\frac{\partial f(a_i)}{\partial u_j}.$
}
\label{fig:backprop-box}
\end{figure}

@@

\begin{figure}[H]
\centerline{
\includegraphics[width=0.49\linewidth]{bp-mlp1.pdf}
\includegraphics[width=0.49\linewidth]{bp-mlp5.pdf}
}
\centerline{
\includegraphics[width=0.89\linewidth]{fig-hidden-recurrence-rnn.pdf}
}
\caption{Top left: graph of feedforward computations in a multi-layer
neural network with one input layer ($x$), two hidden layers ($h_1$ and $h_2$),
one output layer (out), a target $y$, and an error that compares the output
and the target. The synaptic weight matrices $W_1$, $W_2$ and $W_3$ are
the parameters of the neural network.\newline
Top right: back-propagation through the same multi-layer neural network
(downward arrows compute the partial derivative of the error with respect
to every node, i.e., the units value and the parameters).\newline
Bottom: a recurrent neural network (left) and the unfolding in time of the
computation involved in its forward computation. The artificial neurons
(e.g. hidden units grouped under node $s$ with values $s_t$ at time $t$) 
get inputs from other neurons at previous time steps
(this is represented with the black square, for delay of
one time step, on the left). In this way, a recurrent net can map an input sequence
with elements $x_t$ into an output sequence with elements $o_t$, with
each $o_t$ depending on all the previous $x_{t'}$ (for $t'\leq t$). The
same parameters (matrices $U$, $V$, $W$) are used at each time step.
Many other architectures are possible, including a variant in which
the outputs (e.g. words) can be generated according to a distribution 
(the probability of the next word) and used as inputs for the next time step.
The back-propagation algorithm (Figure~\ref{fig:backprop-box})
can be directly applied to the computational graph of the unfolded network
on the right hand side, to compute the derivative of a total error
(at all time steps) with respect to all the states $s_t$ and all the parameters.
}
\label{fig:mlp}
\end{figure}

@@

\begin{figure}[H]
\centerline{
\includegraphics[width=0.49\linewidth]{word-embeddings.png}
\includegraphics[width=0.49\linewidth]{phrase_zoom2.png}
}
\caption{Left: Illustration of word representations learned for modeling
language, non-linearly projected to 2-D for visualization using the
t-SNE algorithm~\citep{VanDerMaaten08}. Right: 2-D representation
of phrases learned by an English-to-French encoder-decoder recurrent
neural network~\citep{Cho-et-al-EMNLP2014}. One can observe that
semantically similar words or sequences of words are  mapped to
nearby representations.
}
\label{fig:word-embeddings}
\end{figure}

@@

\begin{figure}[ht]
\centerline{\includegraphics[width=\linewidth]{caption-generation-Vinyals-et-al.png}}
\caption{Example of captions generated by a recurrent network taking
as extra input the representation extracted by a deep convolutional
net from an image, with the whole system trained to ``translate''
images into captions. Reproduced from~\citet{Vinyals-et-al-arxiv2014}.
}
\label{fig:caption-generation}
\end{figure}

@@

\section{Boxes (TODO)}

>>>>

\documentclass[]{article}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{float}
\parskip 0.1in
\parindent 0.0in
\setcounter{secnumdepth}{1}
\title{Deep Learning}

@@

Deep learning is currently making major advances in solving problems that
have resisted the best attempts of the Artificial Intelligence community
for many years. Deep learning is very good at discovering intricate
structure in large, high-dimensional datasets and is therefore widely
applicable in all of the sciences. For example, it has beaten previous
machine learning techniques at predicting the activity of potential drug
molecules~\citep{Dahl}, detecting new fundamental particles~\citep{particles},
classifying galaxies~\citep{??}, and predicting the effects of mutations in
non-coding DNA on gene expression and disease~\citep{Keung-et-al-2014}. % Frey

@@

%%%%%%% GEOFF %%%%%%%%%%
%GEOFF: Do box explaining backprop equatons
%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\fbox{
\begin{minipage}{\textwidth}
\centerline{
\includegraphics[width=0.33\linewidth]{chain-rule.pdf}
\includegraphics[width=0.33\linewidth]{forward-graph.pdf}
\includegraphics[width=0.33\linewidth]{backward-graph.pdf}
}
\caption{
Left: the chain rule of derivatives tells us how
two small effects (that of a small change of $x$ on $y$, and that of $y$ on $z$)
are composed. A small change $\Delta x$ in $x$
gets transformed first into a small change $\Delta y$ in $y$
by getting multiplied by $\frac{\partial y}{\partial x}$
(that is the definition of partial derivative). Similarly
that creates a change $\Delta z$ in $z$. Inserting one equation
into the other gives the chain rule of derivatives, i.e., how
$\Delta x$ gets turned into $\Delta z$ through multiplication
by the product of $\frac{\partial y}{\partial x}$ and
$\frac{\partial z}{\partial x}$. It also works when $x$, $y$
and $z$ are vectors (and the derivatives are Jacobian matrices). \newline
Middle: many computations, such as the succession of linear and non-linear 
transformations of multi-layer neural networks, can be described as
a graph where each node $i$ computes a quantity $u_i$ (e.g. the
output of an artificial neuron or the value of a parameter such as
a synaptic weight), based on the set of values $a_i$, composed of elements $u_j$ of
predecessors in the graph, i.e., $u_i = f_i(a_i)$. \newline
Right: the chain rule can be generalized to such computational
flow graphs by recursively computing the derivative of the final
node $u_N$ (e.g., the error to be minimized or the output of the neural network)
with respect to every internal node. The basic recursive equation
is
$\frac{\partial u_N}{\partial u_j} = \sum_{i: j \in a_i} \frac{\partial u_N}{\partial u_i}
\frac{\partial f(a_i)}{\partial u_j}.$
}
\end{minipage}
}
\label{fig:backprop-box}
\end{figure}

@@

\begin{figure}[H]
\fbox{
\begin{minipage}{\textwidth}
\centerline{
\includegraphics[width=0.49\linewidth]{bp-mlp1.pdf}
\includegraphics[width=0.49\linewidth]{bp-mlp5.pdf}
}
\centerline{
\includegraphics[width=0.89\linewidth]{fig-hidden-recurrence-rnn.pdf}
}
\caption{Top left: graph of feedforward computations in a multi-layer
neural network with one input layer ($x$), two hidden layers ($h_1$ and $h_2$),
one output layer (out), a target $y$, and an error that compares the output
and the target. The synaptic weight matrices $W_1$, $W_2$ and $W_3$ are
the parameters of the neural network.\newline
Top right: back-propagation through the same multi-layer neural network
(downward arrows compute the partial derivative of the error with respect
to every node, i.e., the units value and the parameters).\newline
Bottom: a recurrent neural network (left) and the unfolding in time of the
computation involved in its forward computation. The artificial neurons
(e.g. hidden units grouped under node $s$ with values $s_t$ at time $t$) 
get inputs from other neurons at previous time steps
(this is represented with the black square, for delay of
one time step, on the left). In this way, a recurrent net can map an input sequence
with elements $x_t$ into an output sequence with elements $o_t$, with
each $o_t$ depending on all the previous $x_{t'}$ (for $t'\leq t$). The
same parameters (matrices $U$, $V$, $W$) are used at each time step.
Many other architectures are possible, including a variant in which
the outputs (e.g. words) can be generated according to a distribution 
(the probability of the next word) and used as inputs for the next time step.
The back-propagation algorithm (Figure~\ref{fig:backprop-box})
can be directly applied to the computational graph of the unfolded network
on the right hand side, to compute the derivative of a total error
(at all time steps) with respect to all the states $s_t$ and all the parameters.
}
\end{minipage}
}
\label{fig:mlp}
\end{figure}

@@

\begin{figure}[H]
\fbox{
\begin{minipage}{\textwidth}
\centerline{
\includegraphics[width=0.49\linewidth]{word-embeddings.png}
\includegraphics[width=0.49\linewidth]{phrase_zoom2.png}
}
\caption{Left: Illustration of word representations learned for modeling
language, non-linearly projected to 2-D for visualization using the
t-SNE algorithm~\citep{VanDerMaaten08}. Right: 2-D representation
of phrases learned by an English-to-French encoder-decoder recurrent
neural network~\citep{Cho-et-al-EMNLP2014}. One can observe that
semantically similar words or sequences of words are  mapped to
nearby representations.
}
\end{minipage}
}
\label{fig:word-embeddings}
\end{figure}

@@

\begin{figure}[ht]
\fbox{
\begin{minipage}{\textwidth}
\centerline{\includegraphics[width=\linewidth]{caption-generation-Vinyals-et-al.png}}
\caption{Example of captions generated by a recurrent network taking
as extra input the representation extracted by a deep convolutional
net from an image, with the whole system trained to ``translate''
images into captions. Reproduced from~\citet{Vinyals-et-al-arxiv2014}.
}
\end{minipage}
}
\label{fig:caption-generation}
\end{figure}

@@

\iffalse
\section{Boxes (TODO)}
